Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
diction

But in Helios, there is a single private ElGamal key that lives on the server. (Note that the
creators of Helios admit this weakness but choose to overlook it, as it is their goal to make
verifiable voting an accessible technology, even with some costs.)

Furthermore, with each of these systems, there is \emph{still} a significant level of trust placed
in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
we must place some trust in that party. In Scantegrity, for example, we must assume that we can
trust at least enough of the secret holders so that the seed cannot be obtained and used
inappropriately.

>>>>

But in Helios, there is a single private ElGamal key that lives on the server. The
authors of Helios acknowledge this weakness but choose to overlook it, as they aim to make
verifiable voting an accessible technology, even with some costs.

Furthermore, with each of these systems, voters must \emph{still} place a significant level of trust
in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
we must place some trust in that party. In Scantegrity, for example, we must assume that we can
trust at least enough of the secret holders so that the seed cannot be obtained and used
inappropriately.
